\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}

### 2016-12-29 latex/article_vol2.tex
Drafting done

\section{Appendix Something} \label{sec:appendix1}
\includepdf[pages=2-4, pagecommand={}, frame=true, noautoscale=true, scale=0.7]{cleanR_toyData.pdf}

\section{Appendix NUMTWO} \label{sec:appendix2}
\hl{Data cleaning with user supplied extensions here}

>>>>

\section{Appendix A: cleaning the toyData data frame} \label{sec:appendix1}
\includepdf[pages=2-4, pagecommand={}, frame=true, noautoscale=true, scale=0.7]{cleanR_toyData.pdf}

\section{Appendix B: User-extended cleaning of
  testData} \label{sec:appendix2}
\includepdf[pages=2-, pagecommand={}, frame=true, noautoscale=true, scale=0.7]{cleanR_testData.pdf}
%\hl{Data cleaning with user supplied extensions here}
